# Code Book
***
This code book summarizes the resulting data fields in > tidydata.txt

# Identifiers
***
* > subject - The ID of the test subject
* > activity - The type of activity performed when the corresponding measurements were taken

# Measurements
***
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r needed headers}
##Reading activity labels and features data
setwd("C:/Users/T430s/Documents/R/DS Coursera/Data/Wk4/UCI HAR Dataset")
features<-read.table("features.txt", header = FALSE)

##Filtering the mean and standard deviation column headers
neededheaders<-subset(features,grepl("mean|std", features[,2]))
neededheaders[,2]
```

# Activity Labels
***
* WALKING (value 1): subject was walking during the test
* WALKING_UPSTAIRS (value 2): subject was walking up a staircase * during the test
* WALKING_DOWNSTAIRS (value 3): subject was walking down a staircase during the test
* SITTING (value 4): subject was sitting during the test
* STANDING (value 5): subject was standing during the test
* LAYING (value 6): subject was laying down during the test